---
title: "Comparing `bulletxtrctr` features to `bulletr`"
author: "Andrew Maloney and Molly McDermott"
date: "7/8/2019"
output: html_document
---

# Features 2017 Data
```{r}

features_2017 <- read_csv("features-hamby.csv") #Reading in csv

features_2017 <- features_2017 %>%
  select(-land1_id, -land2_id) %>% # removing
    filter(study1 != "Cary" & study2 != "Cary") %>%
        filter(study1 == study2) %>%
          select(-study2) %>%
      rename(BarrelB = barrel1, BulletB = bullet1, LandB = land1) %>% # Changed column names
      rename(BarrelA = barrel2, BulletA = bullet2, LandA = land2) %>% # Changed column names
          mutate(study1 = gsub("Hamby44", "Hamby173", study1)) %>% #Chnaging observation name
            mutate(study1 = factor(study1, levels = c("Hamby173", "Hamby252"))) %>% # for ordering principles
      rename(ccf_2017 = ccf, rough_cor_2017 = rough_cor, lag_2017 = lag, D_2017 = D, sd_D_2017 = sd_D, signature_length_2017 = signature_length, overlap_2017 = overlap, matches_2017 = matches, mismatches_2017 = mismatches, cms_2017 = cms, non_cms_2017 = non_cms, sum_peaks_2017 = sum_peaks) # Column names changed for comparing purposes 


#Exploring we see that all lettered Barrels only have bullet equal to 1. No need to worry about a lettered barrel having a bullet 2
# Code will not look like this forever... Duct Tape... Will Dplyr soon...
features_2017 <- features_2017 %>% 
  mutate(BulletA = ifelse(str_detect(BarrelA, "[A-Z]"), BarrelA, BulletA)) %>%
  mutate(BarrelA = ifelse(str_detect(BarrelA, "[A-Z]"), "Unknown", BarrelA))

features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "A"] <- "A") #Assign A to Bullets with column "BarrelA" equalequal to "A"
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "B"] <- "B")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "C"] <- "C")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "D"] <- "D")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "E"] <- "E")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "F"] <- "F")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "G"] <- "G")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "H"] <- "H")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "I"] <- "I")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "J"] <- "J")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "L"] <- "L")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "M"] <- "M")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "N"] <- "N")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "Q"] <- "Q")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "R"] <- "R")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "S"] <- "S")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "U"] <- "U")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "V"] <- "V")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "W"] <- "W")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "X"] <- "X")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "Y"] <- "Y")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "Z"] <- "Z")



features_2017$BarrelA[features_2017$BarrelA == "A"] <- "Unknown" #Group lettered Barrels together into Barrel "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "B"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "C"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "D"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "E"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "F"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "G"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "H"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "I"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "J"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "L"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "M"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "N"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "Q"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "R"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "S"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "U"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "V"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "W"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "X"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "Y"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "Z"] <- "Unknown"

features_2017 <- features_2017 %>% 
  mutate(Bullet1 = paste(study1, BarrelB, BulletB, LandB, sep = "-"),
         Bullet2 = paste(study1, BarrelA, BulletA, LandA, sep = "-"))# Creating ID similar to Heike's 

features_2017 <- features_2017[order(features_2017$study1), ]
#Ordered Set column so that all 173 observations came before 252 observations
# At first glance Hamby173 Barrel 10, Bullet 1, Land 1 seems to be missing

features_2017 <- features_2017 %>% 
  mutate(BarrelB = as.character(BarrelB), 
         BulletA = as.character(BulletA), 
         BulletB = as.character(BulletB), 
         LandA = as.character(LandA), 
         LandB = as.character(LandB))
```

# Comparing 2017 and 2019 after basic cleaning
```{r}
table(comparisons$BarrelA)
table(comparisons$BulletA)
table(comparisons$LandA)

#----------------------------------------------------------------#

table(features_2017$BarrelA)
table(features_2017$BulletA)
table(features_2017$LandA)
```

# Heat Maps
```{r}
library(viridis)

comparisons %>%                          #Comparison heatmap for 2019 data
  filter(!is.na(BarrelA)) %>% 
    filter(!is.na(BarrelB)) %>% 
      group_by(BarrelA, BarrelB, Set) %>% 
        summarise(count = n()) %>% 
  ggplot(aes(x = BarrelA, y = BarrelB))+
    geom_tile(aes(fill = count))+
      scale_fill_viridis(option = "plasma", direction = -1)+ 
        geom_text(aes(label = count))+ 
          ggtitle("Comparison Tiles")+ 
            theme_bw()+ 
              facet_grid(~Set) #Good way to compare graphs below.  Shows how bad "features-hamby.csv" really is. 

comparisons %>% 
  filter(!is.na(BarrelA)) %>% 
    filter(!is.na(BarrelB)) %>% 
      group_by(BarrelA, BarrelB, Set) %>% summarise(count = max(signature_length)) %>% 
  ggplot(aes(x = BarrelA, y = BarrelB))+
    geom_tile(aes(fill = count))+
      scale_fill_viridis(option = "plasma", direction = -1)+ 
        geom_text(aes(label = count))+ 
          ggtitle("Comparison Signature_Length Tiles")+ 
            theme_bw()+
              facet_grid(~Set)



features_2017 %>%                        # features_2017 plot 1
  filter(!is.na(BarrelA)) %>% 
    filter(!is.na(BarrelB)) %>% 
      group_by(BarrelA, BarrelB, study1) %>% 
        summarise(count = n()) %>% 
  ggplot(aes(x = BarrelA, y = BarrelB))+
    geom_tile(aes(fill = count))+
      scale_fill_viridis(option = "plasma", direction = -1)+ 
        geom_text(aes(label = count))+ 
          ggtitle("Comparison Count Version 1")+ 
            theme_bw()+ theme(axis.text.x = element_text(angle = 10))+
              facet_grid(~study1) #Very Promising Results.  This geom_tile/heat_map shows my analysis in visual format.



features_2017 %>%                       # features_2017 plot 2
 filter(!is.na(BarrelA)) %>%
   filter(!is.na(BarrelB)) %>%
     group_by(BarrelA, BarrelB, Bullet1, Bullet2, study1) %>%
      arrange(desc(signature_length_2017)) %>% 
       filter(row_number() == 1) %>% 
                ungroup() %>% 
  group_by(BarrelA, BarrelB, study1) %>%
    summarise(count = n()) %>% 
      ggplot(aes(x = BarrelA, y = BarrelB))+
       geom_tile(aes(fill = count))+
        scale_fill_viridis(option = "plasma", direction = -1)+
          geom_text(aes(label = count))+
            ggtitle("Comparison Count Version 2")+
              theme_bw()+ theme(axis.text.x = element_text(angle = 10))+
                 facet_grid(~study1)
```

We shall use the comparison plot from our 2019 data to help compare our data from 2017.

Looking at features_2017 plot2 we can see that there is missing data on the Barrel-Bullet-Land level.


# Finding Missing Values 
```{r}
# Let's try to find those missing values with an easy way
# Inspiration came from Susan and 
#https://www.r-bloggers.com/r-sorting-a-data-frame-by-the-contents-of-a-column/
#https://www.rdocumentation.org/packages/base/versions/3.6.0/topics/t 

comparisons <- comparisons %>% rename(ccf_2019 = ccf, rough_cor_2019 = rough_cor, lag_2019 = lag, D_2019 = D, sd_D_2019 = sd_D, signature_length_2019 = signature_length, overlap_2019 = overlap, matches_2019 = matches, mismatches_2019 = mismatches, cms_2019 = cms, non_cms_2019 = non_cms, sum_peaks_2019 = sum_peaks)

comparisons_check <- comparisons %>% 
  select(Bullet1, Bullet2) #Remove Columns we wont be using

features_2017_check <- features_2017 %>% 
  select(Bullet1, Bullet2) # Remove Columns we wont be using

finder <- t(apply(comparisons_check,1,sort))
finder <- data.frame(finder)

#Take Transpose and Sort in order... Now we have:
#AB   => AB
#BA   => AB 

finder <- finder[!duplicated(finder),] # Remove duplicates 

finder <- finder %>% 
  rename(Bullet2 = X2, Bullet1 = X1) %>% 
    select(Bullet1, Bullet2) 
      
finder <- anti_join(finder, features_2017_check, by = c("Bullet2")) # Shows what data is missing and if you add Bullet1 to the anti_join you can see all thee missing Unknown|Unknown Comparisons 

head(finder, 10)
```


# Creating Data Frames for feature comparisons
```{r}
#Better version of above method I think, using dplyr

comparisons %>% group_by(Bullet1, Bullet2, ccf_2019) %>% filter(Bullet1 == Bullet2) %>% summarise()

comparisons_for_join <- comparisons %>% 
  filter(ccf_2019 != 1) %>% 
    rowwise() %>%
      mutate(sorter = paste(sort(c(Bullet1, Bullet2)), collapse = "-")) %>% 
        distinct(sorter, .keep_all = T) %>% select(-sorter)

#Assign Comparisons
#Every Row
# create col "sorter", which pastes both cols and sorts in order
# remove all rows with duplicate values in sorter
# no need for column 

comparisons_for_join <- na.omit(comparisons_for_join)# Remove Na
features_2017 <- na.omit(features_2017) # Remove Na

Joined_df <- inner_join(comparisons_for_join, features_2017, by = c("Bullet1", "Bullet2")) #ScatterPlot Comparisons for profile_id version 1
```

# ScatterPlots
```{r}

Joined_df %>% ggplot(aes(x = ccf_2019, y = ccf_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"),show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Cross Correlation")
ggsave("ScatterPlot_6.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = rough_cor_2019, y = rough_cor_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Rough Correlation from two (or more) Aligned Signatures")
ggsave("Scatter_Plot7.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = lag_2019, y = lag_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"),show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Lag from two (or more) Aligned Signatures")
ggsave("Scatter_Plot8.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = D_2019, y = D_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Average Distance between two (or more) Aligned Signatures")
ggsave("Scatter_Plot9.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = sd_D_2019, y = sd_D_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Variation in the Height Measurements between two Aligned Signatures")
ggsave("Scatter_Plot10.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = signature_length_2019, y = signature_length_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("signature_length_2019 Vs signature_length_2017")
ggsave("Scatter_Plot11.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = cms_2019, y = cms_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Consecutively Matching Striation Marks")
ggsave("Scatter_Plot12.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = non_cms_2019, y = non_cms_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Consecutively Non-Matching Striation Marks")
ggsave("Scatter_Plot13.png")
#------------------------------------------------------------------###
Joined_df %>% ggplot(aes(x = sum_peaks_2019, y = sum_peaks_2017))+
  geom_bin2d(aes(fill = match), bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        scale_fill_manual(values = c("#cab2d6","#fdbf6f"))+
          theme_bw()+
            xlab("2019") + ylab("2017")+
              ggtitle("Combined Height of Aligned Striae between two Aligned Signatures")
ggsave("Scatter_Plot14.png")
```

Looking at the scatterplots we can make some observations but before that, let me go over some details.  Two geom_smooth() layers were added.  The blue line represents a lm method and the red line represents the gam method.  Looking at the graphs where each feature is compared with its other version, we see there is no clear linear relationship between x and y.  Over plotting is very bad in this case.  Though, the geom_smooth() methods "lm" and "gam" help a lot.  These two lines make it easier to see what sort of relationship is going on.



```{r}
Hamby_Data_Long_by_YEAR <- Joined_df %>% 
  select(1:2, match, ccf_2019:sum_peaks_2019, ccf_2017:sum_peaks_2017) %>% 
    gather(key="measure", value="value", ccf_2019:sum_peaks_2017) %>%   
      mutate(Year = if_else(grepl("^.+(2017)$", measure), 2017, 2019),
             measure = str_remove(measure, "(_2017|_2019)?$"))
        
Hamby_Data_Long_by_YEAR %>%
    ggplot(aes(value, fill = match))+
      geom_density(position = "identity", alpha = 0.50)+
        facet_wrap(~Year+measure, nrow = 2, scales = "free")+
          scale_fill_brewer(palette = "Paired") + theme_bw()+
            ggtitle("Marginal Density Plots")
ggsave("Density_Plot.png", width = 15, height = 7)
```

```{r}
#Statistical Summary

Joined_df %>% select(ccf_2019:sum_peaks_2019, ccf_2017:sum_peaks_2017) %>% summary()

```


# Bullet Scores
### Currently on hold
```{r eval=FALSE, include=TRUE}
comparisons$rfscore <- predict(rtrees, newdata = comparisons, type = "prob")[,2]
head(comparisons, 500)

Bullet_Scores <- comparisons %>% 
  group_by(BulletA, BulletB) %>% 
    tidyr::nest()

Bullet_Scores <- Bullet_Scores %>% 
  mutate(Bullet_Score = data %>% 
          future_map_dbl(.f = function(d) max(compute_average_scores(land1 = d$LandA, land2 = d$LandB, d$rfscore))))

Bullet_Scores %>% 
  select(-data) %>% 
    arrange(desc(Bullet_Score))


Bullet_Scores <- Bullet_Scores %>% 
  mutate(data = data %>% 
           future_map(.f = function(d){
              d$samepath = bullet_to_land_predict(land1 = d$LandA, land2 = d$LandB, d$rfscore, difference = 0.1)
  d
}))


Bullet_Scores %>% 
  tidyr::unnest(data) 
```

```{r eval=FALSE, include=TRUE}

Bullet_Scores_Examin <- Bullet_Scores %>% 
  tidyr::unnest(data)

Bullet_Scores_Examin %>% 
  filter(samepath == "TRUE")


Bullet_Scores_Examin %>% 
  filter(samepath == "FALSE")
```


# Comparing rfscores
### Currently on hold
```{r eval=FALSE, include=TRUE}
library(gridExtra)

plot1 = comparisons %>%
  filter(BarrelA == 2 & BarrelB == 2) %>% 
    filter(BulletA == 1 & BulletB == 1 ) %>% 
      ggplot(aes(x = LandA, y = LandB, fill = rfscore))+ 
        geom_tile()+ 
          scale_fill_gradient2(low = "#000000", high = "#56B4E9", midpoint = 0.5) +facet_grid(BulletB~BulletA, labeller = "label_both")+ 
            xlab("Land A") + ylab("Land B") + theme(aspect.ratio = 1)+ ggtitle("Same Source and Same Bullet")+ facet_grid(~Set)

plot2 = comparisons %>%
  filter(BarrelA == 2 & BarrelB == 2) %>% 
    filter(BulletA == 1 & BulletB == 2 ) %>% 
      ggplot(aes(x = LandA, y = LandB, fill = rfscore))+ 
        geom_tile()+ 
          scale_fill_gradient2(low = "#000000", high = "#56B4E9", midpoint = 0.5)+
            facet_grid(BulletB~BulletA, labeller = "label_both")+ 
            xlab("Land A") + ylab("Land B") + theme(aspect.ratio = 1)+ 
              ggtitle("Same Source but Different Bullet") + facet_grid(~Set)


plot3 = comparisons %>% 
  filter(BarrelA == 10 & BarrelB == 5) %>% 
    filter(BulletA == 1 & BulletB == 2 ) %>% 
      ggplot(aes(x = LandA, y = LandB, fill = rfscore))+ 
        geom_tile()+ 
          scale_fill_gradient2(low = "#000000", high = "#56B4E9", midpoint = 0.5)+
            facet_grid(BulletB~BulletA, labeller = "label_both")+ 
            xlab("Land A") + ylab("Land B") + theme(aspect.ratio = 1)+
              ggtitle("Different Source") + facet_grid(~Set)

grid.arrange(plot1, plot2, plot3, ncol = 2)

```






