---
title: "Refit Analysis"
author: "Andrew Maloney"
date: "6/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown
```{r}
#Loading Packages
#Will most likely add more
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(randomForest)
library(ggplot2)
library(readr)
library(furrr)
library(stringr)
library(dichromat)
library(future)
library(gridExtra)
library(tidyr)
options(future.globals.maxSize = 4*1024*1024*1024)
#data_dir <- "/media/Raven/REU_Refit"


```

```{r eval=FALSE, include=TRUE}
# Reading in Hamby_173
df <- tibble(path = list.files(path = "Hamby_173", 
                               pattern = ".x3p", recursive = T, 
                               full.names = T)) %>% 
  mutate(Barrel = str_extract(path, "(Unknown|Barrel)\\d{0,2}") %>% 
           str_remove("Barrel"), 
         Bullet = str_extract(path, "Bullet[12A-Z]") %>% 
           str_remove("Bullet"),
         Land = str_extract(path, "land\\d{1}") %>% 
           str_remove("land")) %>% 
  mutate(Set = "Hamby173") %>%
  mutate(x3p = map(path, read_x3p)) %>%
 
  mutate(x3p = map(x3p, ~x3p_m_to_mum(.) %>% y_flip_x3p()))

# Reading in Hamby_252
df2 <- tibble(path = list.files(path = "Hamby_252", 
                                pattern = ".x3p", recursive = T, 
                                full.names = T)) %>% 
  mutate(Barrel = str_extract(path, "(Unknown|Barrel)\\d{0,2}") %>% 
           str_remove("Barrel"), 
         Bullet = str_extract(path, "Bullet[12A-Z]") %>% 
           str_remove("Bullet"), 
         Land = str_extract(path, "Bullet [12A-Z]-[123456]") %>% 
           str_remove("Bullet [12A-Z]-")) %>% 
  mutate(Set = "Hamby252") %>%
  mutate(x3p = map(path,read_x3p))  %>%
  # Adjust orientation
  mutate(x3p = map(x3p, ~x3p_m_to_mum(.) %>% rotate_x3p(angle = -90) %>% y_flip_x3p()))
# One big data set - easier to debug the code if you do everything in one big go.
hamby <- bind_rows(df, df2) 
hamby <- hamby %>%
  mutate(id = paste(Set, Barrel, Bullet, Land, sep = "-")) %>%
  select(id, Set, Barrel, Bullet, Land, x3p, path)
rm(df, df2)
```

# Cross Sections look good.
```{r eval=FALSE, include=TRUE}
plan(multicore) # use all the cores at once
hamby <- hamby %>%
  mutate(
    CrossSection = map_dbl(x3p, x3p_crosscut_optimize, minccf = 0.9, span = 0.3, percent_missing = 25))

head(select(hamby, -path, -x3p), 5)
#hamby %>% arrange(desc(CrossSection))

plot1 = hamby %>% 
  filter(Barrel != "Unknown") %>% 
    ggplot(aes(x = Barrel, y = CrossSection, fill = Bullet))+ 
      geom_boxplot()+
          ggtitle("Barrels 1-10")

plot2 = hamby %>% 
  filter(Barrel == "Unknown") %>% 
    ggplot(aes(x = Barrel, y = CrossSection, fill = Bullet))+ 
      geom_boxplot()+
          ggtitle("Barrel Unknown")

grid.arrange(plot1, plot2)
```

Looking at the Boxplot for Barrels 1-10, we can see the inter-quartile ranges seem to be roughly the same for each Bullet.  For Barrels 1-10, Bullet 2 seems to have higher values than Bullet 1.  Barrels 6 and 7 have the largest whiskers.  Barrel 1, Bullet 1 has the smallest inter-quartile range and Barrel 9, Bullet 2 has the largest interquartile range.  There is one apparent outlier for Barrel 10, Bullet 1.  This CrossSection Value is not high enough for concern when looking at all Barrels but should be examined separately.

Looking at the Boxplot for Barrel "Unknown" we can see an apparent outlier for Bullet B.  This CrossSection value is 400.  Unlike with Barrels 1-10 we can see the Bullets for Barrel "Unknown" have noticeably  more lower whiskers.


```{r eval=FALSE, include=TRUE}
#Cross Sections
hamby <- hamby %>% 
  mutate(CrossCut = map2(.x = x3p, .y = CrossSection, .f = x3p_crosscut))

crosscuts <- select(hamby, -path, -x3p) %>% 
      tidyr::unnest(CrossCut)

crosscuts %>% 
  arrange(desc(CrossSection))
```

Note: For Hamby173 barrels 1, 2, and 4 for bullet 1 seem to have higher crosscut values plotted.  For Hamby173 barrel 1, bullet 2 seems to have a higher crosscut values plotted. There doesn't seem to be any noticeably low values for Hamby173.

Note: For Hamby 252 barrel 10 and 2, bullet 1 has high crosscut values plotted.  There also seems to be some low crosscut values plotted as well. 

```{r}
#Looking at CrossCuts to see any issues

crosscuts %>%
  filter(Barrel != "Unknown" & Set == "Hamby173") %>% 
    ggplot(data = ., aes(x = x, y = value, color = Land)) + 
      geom_line() + 
        facet_grid(Set + paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))

crosscuts %>%
  filter(Barrel != "Unknown" & Set == "Hamby252") %>% 
    ggplot(data = ., aes(x = x, y = value, color = Land)) + 
      geom_line() + 
        facet_grid(Set + paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))

crosscuts %>% 
  filter(Set == "Hamby173" & Barrel == "Unknown") %>%
    ggplot(aes(x = x, y = value)) + 
      geom_line() +
        facet_grid(Bullet~Land, labeller="label_both") +
          theme_bw()+ ggtitle("Barrel Unknown for Hamby173")

crosscuts %>% 
  filter(Set == "Hamby252" & Barrel == "Unknown") %>%
    ggplot(aes(x = x, y = value)) + 
      geom_line() +
        facet_grid(Bullet~Land, labeller="label_both") +
          theme_bw()+ ggtitle("Barrel Unknown for Hamby252")

crosscuts %>% filter(id == "Hamby252-Unknown-B-2") %>% 
  ggplot(aes(x = x, y = value))+
    geom_line()+
      facet_grid(Bullet~Land + Set, labeller = "label_both")+
        theme_bw() + ggtitle("High CrossSection Bullet B")
```

Looking at the CrossCuts we can see the side profile for a bullets land impression for every barrel in Hamby173 and Hamby252.  For most of the CrossCuts the shoulders can be clearly identified but there are some that can not be "clearly" identified due to possbile tank rash, pitting, or scans that do not meet the standards that forensic analysis require.  I can not say for certain if there are scans that should be excluded.  I used FIX3P to examine the "groove to groove" scans and noticed considerable tank rash on some of the scans.  There was some noticeable pitting as well but I only felt it was a concern when the pitting was concentrated in the center of the "groove to groove" scan.

When looking at the Crosscuts we can see most have noticeable curvature.  There are some scans that do not and these scans can look like a flat line or even a traingle... I Have made note of these particular scans as well.  


# Groove Loader
```{r eval=FALSE, include=TRUE}
#Grooves
saved_grooves_location <- "V2H173_H252_Grooves_data.rda"
if (file.exists(saved_grooves_location)) {
  hamby$Grooves <- readRDS(saved_grooves_location)
} else {
  hamby <- hamby %>% 
    mutate(Grooves = CrossCut %>% 
             map(.f = cc_locate_grooves, 
                        method = "rollapply", smoothfactor = 15, return_plot = T))  # use plot so that the shiny app works...
}

grooves <- hamby %>% tidyr::unnest(Grooves)

head(grooves, 10)

head(select(hamby, -path, -x3p, -CrossCut), 5)
```


# Examining Groove Cut Offs
```{r eval=FALSE, include=TRUE}
Hamby_test <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 6)

Hamby_test2 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 3 & Bullet == 1)

Hamby_test3 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 1 & Bullet == 1)

Hamby_test4 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 9 & Bullet == 2)

Hamby_test5 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == "Unknown") %>% 
      filter(Bullet == "B" | Bullet == "S" | Bullet == "U")

Hamby_test6 <- hamby %>% 
  filter(Set == "Hamby173") %>% 
    filter(Barrel == 3 & Bullet == 2)

Hamby_test7 <- hamby %>% 
  filter(Set == "Hamby173") %>% 
    filter(Barrel == "Unknown") %>% 
      filter(Bullet == "B" | Bullet == "E" | Bullet == "U")


gridExtra::grid.arrange(Hamby_test$Grooves[[1]]$plot,
                        Hamby_test$Grooves[[7]]$plot,
                         Hamby_test2$Grooves[[4]]$plot,
                         Hamby_test3$Grooves[[6]]$plot,
                         Hamby_test4$Grooves[[4]]$plot,
                         Hamby_test5$Grooves[[2]]$plot,
                         Hamby_test5$Grooves[[10]]$plot,
                        nrow = 2)
                        
                        

                        
gridExtra::grid.arrange(Hamby_test6$Grooves[[1]]$plot,
                        Hamby_test7$Grooves[[3]]$plot,
                        Hamby_test7$Grooves[[15]]$plot,
                        Hamby_test7$Grooves[[12]]$plot,
                        nrow = 2)

rm(Hamby_test, Hamby_test2, Hamby_test3, Hamby_test4, Hamby_test5, Hamby_test6, Hamby_test7 )
```


# When run in interactive mode, a shiny app can be used to set smarter grooves.
# Groove Identifications by: Andrew Maloney
# Using Shiny App
```{r get-grooves-interactive, eval=FALSE, include=TRUE}
library(shiny)
if (file.exists(saved_grooves_location)) {
  hamby$Grooves <- readRDS(saved_grooves_location)
}
if (interactive()) { # only run when you're manually running chunks... don't run when the whole document is compiled.
  shinyApp(
    ui = fluidPage(
      selectInput("k", "Investigate kth plot:",
                  selected = 1,
                  choices = (1:length(hamby$Grooves)) %>% set_names(hamby$id)
      ),
      textOutput("groovelocations"),
      actionButton("confirm", "Confirm"),
      actionButton("save", "Save"),
      plotOutput("groovePlot", click = "plot_click"),
      verbatimTextOutput("info")
    ),
    
    server = function(input, output, session) {
      output$groovePlot <- renderPlot({
        k <- as.numeric(input$k)
        p <- hamby$Grooves[[k]]$plot
        
        p
      })
      output$groovelocations <- renderText({
        paste(
          "Left Groove: ", hamby$Grooves[[as.numeric(input$k)]]$groove[1],
          " Right Groove: ", hamby$Grooves[[as.numeric(input$k)]]$groove[2]
        )
      })
      observeEvent(input$confirm, {
        cat(paste(hamby$id[as.numeric(input$k)], "\n"))
        updateSelectInput(session, "k", "Investigate kth plot:",
                          selected = as.numeric(input$k) + 1,
                          choices = (1:length(hamby$Grooves)) %>% set_names(hamby$id)
        )
      })
      observeEvent(input$save, {
        saveRDS(hamby$Grooves, file = saved_grooves_location)
        message("groove data saved\n")
      })
      
      observeEvent(input$plot_click, {
        k <- as.numeric(input$k)
        xloc <- input$plot_click$x
        
        gr <- hamby$Grooves[[k]]$groove
        if (abs(gr[1] - xloc) < abs(gr[2] - xloc)) {
          hamby$Grooves[[k]]$groove[1] <<- xloc
        } else {
          hamby$Grooves[[k]]$groove[2] <<- xloc
        }
        output$groovePlot <- renderPlot({
          k <- as.numeric(input$k)
          p <- hamby$Grooves[[k]]$plot +
            geom_vline(xintercept = hamby$Grooves[[k]]$groove[1], colour = "green") +
            geom_vline(xintercept = hamby$Grooves[[k]]$groove[2], colour = "green")
          
          p
        })
      })
      output$info <- renderText({
        paste0("x=", input$plot_click$x, "\ny=", input$plot_click$y)
      })
    },
    options = list(height = 500)
  )
  saveRDS(hamby$Grooves, file = saved_grooves_location)
} else {
  if (!file.exists(saved_grooves_location)) {
    message("run script in interactive mode to fix grooves")
  } else {
    hamby$Grooves <- readRDS(saved_grooves_location)
  }
}


#Test Some Grooves(performed:06/12/19)
```

```{r eval=FALSE, include=TRUE}
#Signatures
hamby <- hamby %>% 
  mutate(Signatures = map2(.x = CrossCut, .y = Grooves, .f = cc_get_signature, span = 0.75, span2 = .03)) 

Signatures <- hamby %>% 
  select(id, Set, Barrel, Bullet, Land, Signatures) %>% 
    tidyr::unnest()
```

```{r}
#Looking for major issues - grooves not set correctly (large deviations at beginning or end of a line)

Signatures %>%
  filter(Barrel != "Unknown") %>% 
ggplot(data = ., aes(x = x, y = sig, color = Land)) + 
  geom_line()+
  facet_grid(Set + paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel)) # put the barrels in the right order

Signatures %>%
  filter(Set == "Hamby173") %>%
  filter(Barrel == "Unknown") %>% 
ggplot(data = ., aes(x = x, y = sig, color = Land)) + 
  geom_line()+
  facet_wrap(paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel), ncol = 4)

Signatures %>%
  filter(Set == "Hamby252") %>%
  filter(Barrel == "Unknown") %>% 
ggplot(data = ., aes(x = x, y = sig, color = Land)) + 
  geom_line()+
  facet_wrap(paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel), ncol = 4)

```

Examining the Signature Profiles we can see for barrels 1-10, for both Hamby173 + Hamby252, that the signatures for lands 1-6 are aligned pretty well.  There seems to be some noticeable deviations at the beginning and end for Barrels 1-10 in both sets. I looked at the groove to groove scans using FIX3P and these spikes at the beginning and end for Barrels 1 and 10 can be identified.  Groove locations seem to be set correctly for these lands.  

There is some noticeable missing data for Signature comparisons [Hamby252/Bullet1] when filling by Bullet.  This is hard to see when filling by the Lands.

We also examine the number of consecutively matching peaks in signatures for two aligned lands.(Case Validation Paper)

Groove Identifications Approved

```{r eval=FALSE, warning=FALSE, include=TRUE}
comparisons <- crossing(Bullet1 = hamby$id, Bullet2 = hamby$id) %>%
  left_join(nest(hamby, -id) %>% magrittr::set_names(c("Bullet1", "Bullet1_data"))) %>%
  left_join(nest(hamby, -id) %>% magrittr::set_names(c("Bullet2", "Bullet2_data"))) %>%
  mutate(Set1 = str_extract(Bullet1, "Hamby\\d{2,3}"),
         Set2 = str_extract(Bullet2, "Hamby\\d{2,3}")) %>%
  filter(Set1 == Set2) %>% # Get rid of cross-set comparisons for now...
  select(-matches("Set"))
```

```{r eval=FALSE, include=TRUE}
#plan(multicore(workers = availableCores(constraints = 8)))

get_sig <- function(data) {
  map(data$Signatures, "sig")
}
comparisons <- comparisons %>%
  mutate(sig1 = map(Bullet1_data, get_sig), sig2 = purrr::map(Bullet2_data, get_sig))

plan(multicore)

comparisons <- comparisons %>%
  mutate(Aligned = map2(sig1, sig2, ~sig_align(unlist(.x), unlist(.y)))) # Getting Aligned signatures

# Get striae
comparisons <- comparisons %>%
  mutate(Striae = map(Aligned, sig_cms_max)) # Obtaining Striae

saveRDS(select(comparisons, -Bullet1_data, -Bullet2_data), file = "Hamby_173_252_Comparisons.rda")
```

# Extracting features
```{r eval=FALSE, include=TRUE}
comparisons <- comparisons %>% 
  select(-Bullet1_data, -Bullet2_data)

comparisons <- comparisons %>% 
  mutate(features = map2(.x = Aligned, .y = Striae, .f = extract_features_all, resolution = 1.5625)) #ObtainingFeatures

comparisons <- comparisons %>% 
  mutate(Legacy_Features = map(Striae, extract_features_all_legacy, resolution = 1.5625)) # Obtaining feature leacy

comparisons <- comparisons %>% 
  tidyr::unnest(Legacy_Features) # Extracting feature legacy
```


# Creating Columns for organization and for future plotting purposes.
```{r}
comparisons <- comparisons %>% 
  mutate(Set = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\1", Bullet2)) # Creating columns from IDs
comparisons <- comparisons %>% 
  mutate(BarrelA = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\2", Bullet2))
comparisons <- comparisons %>% 
  mutate(BarrelB = gsub("(Hamby173|Hamby252)-([0-9]{0,2}|Unknown)-([1-2A-Z])-([1-6])", "\\2", Bullet1))
comparisons <- comparisons %>% 
  mutate(BulletA = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\3", Bullet2))
comparisons <- comparisons %>% 
  mutate(BulletB = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\3", Bullet1))
comparisons <- comparisons %>% 
  mutate(LandA = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\4", Bullet2))
comparisons <- comparisons %>% 
  mutate(LandB = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\4", Bullet1))
head(comparisons, 500)
```

# Features 2017 Data
```{r}

features_2017 <- read_csv("features-hamby.csv") #Reading in csv

features_2017 <- features_2017 %>%
  select(-land1_id, -land2_id) %>% # removing
    filter(study1 != "Cary" & study2 != "Cary") %>%
        filter(study1 == study2) %>%
          select(-study2) %>%
      rename(BarrelB = barrel1, BulletB = bullet1, LandB = land1) %>% # Changed column names
      rename(BarrelA = barrel2, BulletA = bullet2, LandA = land2) %>% # Changed column names
          mutate(study1 = gsub("Hamby44", "Hamby173", study1)) %>% #Chnaging observation name
            mutate(study1 = factor(study1, levels = c("Hamby173", "Hamby252"))) %>% # for ordering principles
      rename(ccf2 = ccf, rough_cor2 = rough_cor, lag2 = lag, D2 = D, sd_D2 = sd_D, signature_length2 = signature_length, overlap2 = overlap, matches2 = matches, mismatches2 = mismatches, cms2x = cms, non_cms2 = non_cms, sum_peaks2 = sum_peaks) # Column names changed for comparing purposes 


#Exploring we see that all lettered Barrels only have bullet equal to 1. No need to worry about a lettered barrel having a bullet 2
# Code will not look like this forever... Duct Tape... Will Dplyr soon...

features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "A"] <- "A") #Assign A to Bullets with column "BarrelA" equalequal to "A"
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "B"] <- "B")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "C"] <- "C")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "D"] <- "D")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "E"] <- "E")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "F"] <- "F")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "G"] <- "G")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "H"] <- "H")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "I"] <- "I")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "J"] <- "J")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "L"] <- "L")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "M"] <- "M")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "N"] <- "N")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "Q"] <- "Q")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "R"] <- "R")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "S"] <- "S")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "U"] <- "U")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "V"] <- "V")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "W"] <- "W")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "X"] <- "X")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "Y"] <- "Y")
features_2017 <- within(features_2017, BulletA[BulletA == 1 & BarrelA == "Z"] <- "Z")



features_2017$BarrelA[features_2017$BarrelA == "A"] <- "Unknown" #Group lettered Barrels together into Barrel "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "B"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "C"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "D"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "E"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "F"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "G"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "H"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "I"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "J"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "L"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "M"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "N"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "Q"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "R"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "S"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "U"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "V"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "W"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "X"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "Y"] <- "Unknown"
features_2017$BarrelA[features_2017$BarrelA == "Z"] <- "Unknown"

features_2017 <- features_2017 %>% 
  mutate(Bullet1 = paste(study1, BarrelB, BulletB, LandB, sep = "-"),
         Bullet2 = paste(study1, BarrelA, BulletA, LandA, sep = "-"))# Creating ID similar to Heike's 

features_2017 <- features_2017[order(features_2017$study1), ]
#Ordered Set column so that all 173 observations came before 252 observations
# At first glance Hamby173 Barrel 10, Bullet 1, Land 1 seems to be missing

features_2017 <- features_2017 %>% 
  mutate(BarrelB = as.character(BarrelB), 
         BulletA = as.character(BulletA), 
         BulletB = as.character(BulletB), 
         LandA = as.character(LandA), 
         LandB = as.character(LandB))
```

# Comparing 2017 and 2019 after basic cleaning
```{r}
table(comparisons$BarrelA)
table(comparisons$BulletA)
table(comparisons$LandA)

#----------------------------------------------------------------#

table(features_2017$BarrelA)
table(features_2017$BulletA)
table(features_2017$LandA)
```

# Heat Maps
```{r}
library(viridis)

comparisons %>%                          #Comparison heatmap for 2019 data
  filter(!is.na(BarrelA)) %>% 
    filter(!is.na(BarrelB)) %>% 
      group_by(BarrelA, BarrelB, Set) %>% 
        summarise(count = n()) %>% 
  ggplot(aes(x = BarrelA, y = BarrelB))+
    geom_tile(aes(fill = count))+
      scale_fill_viridis(option = "plasma", direction = -1)+ 
        geom_text(aes(label = count))+ 
          ggtitle("Comparison Tiles")+ 
            theme_bw()+ 
              facet_grid(~Set) #Good way to compare graphs below.  Shows how bad "features-hamby.csv" really is. 

comparisons %>% 
  filter(!is.na(BarrelA)) %>% 
    filter(!is.na(BarrelB)) %>% 
      group_by(BarrelA, BarrelB, Set) %>% summarise(count = max(signature_length)) %>% 
  ggplot(aes(x = BarrelA, y = BarrelB))+
    geom_tile(aes(fill = count))+
      scale_fill_viridis(option = "plasma", direction = -1)+ 
        geom_text(aes(label = count))+ 
          ggtitle("Comparison Signature_Length Tiles")+ 
            theme_bw()+
              facet_grid(~Set)



features_2017 %>%                        # features_2017 plot 1
  filter(!is.na(BarrelA)) %>% 
    filter(!is.na(BarrelB)) %>% 
      group_by(BarrelA, BarrelB, study1) %>% 
        summarise(count = n()) %>% 
  ggplot(aes(x = BarrelA, y = BarrelB))+
    geom_tile(aes(fill = count))+
      scale_fill_viridis(option = "plasma", direction = -1)+ 
        geom_text(aes(label = count))+ 
          ggtitle("Comparison Count Version 1")+ 
            theme_bw()+ theme(axis.text.x = element_text(angle = 10))+
              facet_grid(~study1) #Very Promising Results.  This geom_tile/heat_map shows my analysis in visual format.



features_2017 %>%                       # features_2017 plot 2
 filter(!is.na(BarrelA)) %>%
   filter(!is.na(BarrelB)) %>%
     group_by(BarrelA, BarrelB, Bullet1, Bullet2, study1) %>%
      arrange(desc(signature_length2)) %>% 
       filter(row_number() == 1) %>% 
                ungroup() %>% 
  group_by(BarrelA, BarrelB, study1) %>%
    summarise(count = n()) %>% 
      ggplot(aes(x = BarrelA, y = BarrelB))+
       geom_tile(aes(fill = count))+
        scale_fill_viridis(option = "plasma", direction = -1)+
          geom_text(aes(label = count))+
            ggtitle("Comparison Count Version 2")+
              theme_bw()+ theme(axis.text.x = element_text(angle = 10))+
                 facet_grid(~study1)
```

We shall use the comparison plot from our 2019 data to help compare our data from 2017.

Looking at features_2017 plot2 we can see that there is missing data on the Barrel-Bullet-Land level.


# Finding Missing Values 
```{r}
# Let's try to find those missing values with an easy way
# Inspiration came from Susan and 
#https://www.r-bloggers.com/r-sorting-a-data-frame-by-the-contents-of-a-column/
#https://www.rdocumentation.org/packages/base/versions/3.6.0/topics/t 

comparisons_check <- comparisons %>% 
  select(Bullet1, Bullet2) #Remove Columns we wont be using

features_2017_check <- features_2017 %>% 
  select(Bullet1, Bullet2) # Remove Columns we wont be using

finder <- t(apply(comparisons_check,1,sort))
finder <- data.frame(finder)

#Take Transpose and Sort in order... Now we have:
#AB   => AB
#BA   => AB 

finder <- finder[!duplicated(finder),] # Remove duplicates 

finder <- finder %>% 
  rename(Bullet2 = X2, Bullet1 = X1) %>% 
    select(Bullet1, Bullet2) 
      
finder <- anti_join(finder, features_2017_check, by = c("Bullet2")) # Shows what data is missing and if you add Bullet1 to the anti_join you can see all thee missing Unknown|Unknown Comparisons 
```


# Creating Data Frames for feature comparisons
```{r}
#Better version of above method I think, using dplyr

comparisons %>% group_by(Bullet1, Bullet2, ccf) %>% filter(Bullet1 == Bullet2) %>% summarise()

comparisons_for_join <- comparisons %>% 
  filter(ccf != 1) %>% 
    rowwise() %>%
      mutate(sorter = paste(sort(c(Bullet1, Bullet2)), collapse = "-")) %>% 
        distinct(sorter, .keep_all = T) %>% select(-sorter)

#Assign Comparisons
#Every Row
# create col "sorter", which pastes both cols and sorts in order
# remove all rows with duplicate values in sorter
# no need for column 

comparisons_for_join <- na.omit(comparisons_for_join)# Remove Na
features_2017 <- na.omit(features_2017) # Remove Na

Joined_df <- inner_join(comparisons_for_join, features_2017, by = c("Bullet1", "Bullet2")) #ScatterPlot Comparisons for profile_id version 1
```

# ScatterPlots
```{r}
library(ggExtra)

Joined_df %>% ggplot(aes(x = ccf, y = ccf2))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        ggtitle("ccf Vs ccf2")

Joined_df %>% ggplot(aes(x = rough_cor, y = rough_cor2))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("rough_cor Vs rough_cor2")

Joined_df %>% ggplot(aes(x = cms, y = cms2x))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("cms Vs cms2")

Joined_df %>% ggplot(aes(x = sum_peaks, y = sum_peaks2))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("sum_peaks Vs sum_peaks2")

Joined_df %>% ggplot(aes(x = signature_length, y = signature_length2))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("signature_length Vs signature_length2")

Joined_df %>% ggplot(aes(x = D, y = D2))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("Distance Vs Distance2")

Joined_df %>% ggplot(aes(x = non_cms, y = non_cms2))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("non_cms vs noncms2")


#-----------------------------------------------------------------------------#
# Here is a subset of data plotted.  I did this because of all the overplotting.  Wanted to see if there was a relationship
Joined_df %>% 
  filter(BarrelA.y == 1 | BarrelA.y == 2 | BarrelA.y == 3) %>%
     ggplot(aes(x = ccf, y = ccf2))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("Avoid overplotting ccf Vs ccf2")

Joined_df %>% 
  filter(BarrelA.y == 1 | BarrelA.y == 2 | BarrelA.y == 3) %>%
     ggplot(aes(x = cms, y = cms2x))+
  geom_bin2d(bins = 65)+
  geom_smooth(method = lm)+
      geom_smooth(aes(colour = "red"), show.legend = FALSE)+
        theme_bw()+
        ggtitle("Avoid overplotting ccf Vs ccf2")
    
```

Looking at the scatterplots we can make some observations but before that, let me go over some details.  Two geom_smooth() layers were added.  The blue line represents a lm method and the red line represents the gam method.  Looking at the graphs where each feature is compared with its other version, we see there is no clear linear relationship between x and y.  Over plotting is very bad in this case.  Though, the geom_smooth() methods "lm" and "gam" help a lot.  These two lines make it easier to see what sort of relationship is going on.



```{r}
HambyDataLong <- gather(Joined_df, key="measure", value="value", c("ccf", "cms", "non_cms", "matches", "mismatches", "D", "sum_peaks"))

HambyDataLong2 <- gather(Joined_df, key="measure", value="value", c("ccf2", "cms2x", "non_cms2", "matches2", "mismatches2", "D2", "sum_peaks2"))
      
HambyDataLong %>% 
    ggplot(aes(value, fill = match))+
      geom_density(position = "identity", alpha = 0.50)+
        facet_wrap(~measure, ncol = 4, scale = "free")+
          scale_fill_brewer(palette = "Paired") + theme_bw()+
            ggtitle("Marginal Density for Features 2019 Data")

HambyDataLong %>% 
    ggplot(aes(value, fill = match))+
      geom_density(position = "identity", alpha = 0.50)+
        facet_wrap(~measure + study1, ncol = 4, scale = "free")+
          scale_fill_brewer(palette = "Paired") + theme_bw()+
            ggtitle("Marginal Density for Features")

HambyDataLong2 %>% 
    ggplot(aes(value, fill = match))+
      geom_density(position = "identity", alpha = 0.50)+
        facet_wrap(~measure, ncol = 4, scale = "free")+
          scale_fill_brewer(palette = "Paired") + theme_bw()+
            ggtitle("Marginal Density for Features")

HambyDataLong2 %>% 
    ggplot(aes(value, fill = match))+
      geom_density(position = "identity", alpha = 0.50)+
        facet_wrap(~measure + study1, ncol = 4, scale = "free")+
          scale_fill_brewer(palette = "Paired") + theme_bw()+
            ggtitle("Marginal Density for Features 2017")
```

```{r}
#Statistical Summary

Joined_df %>% select(ccf, ccf2, cms, cms2x, D, D2, matches, matches2, mismatches, mismatches2, non_cms, non_cms2, sum_peaks, sum_peaks2) %>% summary()

```


The statistical summary is also concerning because some of the features such as D and D2 differ by a lot.





