---
title: "Untitled"
author: "Andrew Maloney"
date: "6/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown
```{r}
#Loading Packages
#Will most likely add more
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(randomForest)
library(ggplot2)
library(readr)
library(furrr)
library(stringr)
library(dichromat)
library(future)
library(gridExtra)
library(tidyr)
options(future.globals.maxSize = 4*1024*1024*1024)
#data_dir <- "/media/Raven/REU_Refit"
```

```{r}
# Reading in Hamby_173
df <- tibble(path = list.files(path = "Hamby_173", 
                               pattern = ".x3p", recursive = T, 
                               full.names = T)) %>% 
  mutate(Barrel = str_extract(path, "(Unknown|Barrel)\\d{0,2}") %>% 
           str_remove("Barrel"), 
         Bullet = str_extract(path, "Bullet[12A-Z]") %>% 
           str_remove("Bullet"),
         Land = str_extract(path, "land\\d{1}") %>% 
           str_remove("land")) %>% 
  mutate(Set = "Hamby173") %>%
  mutate(x3p = future_map(path, read_x3p)) %>%
 
  mutate(x3p = future_map(x3p, ~x3p_m_to_mum(.) %>% y_flip_x3p()))

# Reading in Hamby_252
df2 <- tibble(path = list.files(path = "Hamby_252", 
                                pattern = ".x3p", recursive = T, 
                                full.names = T)) %>% 
  mutate(Barrel = str_extract(path, "(Unknown|Barrel)\\d{0,2}") %>% 
           str_remove("Barrel"), 
         Bullet = str_extract(path, "Bullet[12A-Z]") %>% 
           str_remove("Bullet"), 
         Land = str_extract(path, "Bullet [12A-Z]-[123456]") %>% 
           str_remove("Bullet [12A-Z]-")) %>% 
  mutate(Set = "Hamby252") %>%
  mutate(x3p = future_map(path,read_x3p))  %>%
  # Adjust orientation
  mutate(x3p = future_map(x3p, ~x3p_m_to_mum(.) %>% rotate_x3p(angle = -90) %>% y_flip_x3p()))
# One big data set - easier to debug the code if you do everything in one big go.
hamby <- bind_rows(df, df2) 
hamby <- hamby %>%
  mutate(id = paste(Set, Barrel, Bullet, Land, sep = "-")) %>%
  select(id, Set, Barrel, Bullet, Land, x3p, path)
rm(df, df2)
```

# Cross Sections look good.
```{r}
plan(multicore) # use all the cores at once
hamby <- hamby %>%
  mutate(
    CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, minccf = 0.9, span = 0.3, percent_missing = 25))

head(select(hamby, -path, -x3p), 5)
#hamby %>% arrange(desc(CrossSection))

plot1 = hamby %>% 
  filter(Barrel != "Unknown") %>% 
    ggplot(aes(x = Barrel, y = CrossSection, fill = Bullet))+ 
      geom_boxplot()+
          ggtitle("Barrels 1-10")

plot2 = hamby %>% 
  filter(Barrel == "Unknown") %>% 
    ggplot(aes(x = Barrel, y = CrossSection, fill = Bullet))+ 
      geom_boxplot()+
          ggtitle("Barrel Unknown")

grid.arrange(plot1, plot2)

```

Looking at the Boxplot for Barrels 1-10, we can see the inter-quartile ranges seem to be roughly the same for each Bullet.  For Barrels 1-10, Bullet 2 seems to have higher values than Bullet 1.  Barrels 6 and 7 have the largest whiskers.  Barrel 1, Bullet 1 has the smallest inter-quartile range and Barrel 9, Bullet 2 has the largest interquartile range.  There is one apparent outlier for Barrel 10, Bullet 1.  This CrossSection Value is not high enough for concern when looking at all Barrels but should be examined separately.

Looking at the Boxplot for Barrel "Unknown" we can see an apparent outlier for Bullet B.  This CrossSection value is 400.  Unlike with Barrels 1-10 we can see the Bullets for Barrel "Unknown" have noticeably  more lower whiskers.


```{r}
#Cross Sections
hamby <- hamby %>% 
  mutate(CrossCut = future_map2(.x = x3p, .y = CrossSection, .f = x3p_crosscut))

crosscuts <- select(hamby, -path, -x3p) %>% 
      tidyr::unnest(CrossCut)

crosscuts %>% 
  arrange(desc(CrossSection))
```

#### For Hamby173 barrels 1, 2, and 4 for bullet 1 seem to have higher crosscut values plotted.  For Hamby173 barrel 1, bullet 2 seems to have a higher crosscut values plotted. There doesn't seem to be any noticeably low values for Hamby173.

#### For Hamby 252 barrel 10 and 2, bullet 1 has high crosscut values plotted.  There also seems to be some low crosscut values plotted as well. 

```{r}
#Looking at CrossCuts to see any issues

crosscuts %>%
  filter(Barrel != "Unknown" & Set == "Hamby173") %>% 
    ggplot(data = ., aes(x = x, y = value, color = Land)) + 
      geom_line() + 
        facet_grid(Set + paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))

crosscuts %>%
  filter(Barrel != "Unknown" & Set == "Hamby252") %>% 
    ggplot(data = ., aes(x = x, y = value, color = Land)) + 
      geom_line() + 
        facet_grid(Set + paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))

crosscuts %>% 
  filter(Set == "Hamby173" & Barrel == "Unknown") %>%
    ggplot(aes(x = x, y = value)) + 
      geom_line() +
        facet_grid(Bullet~Land, labeller="label_both") +
          theme_bw()+ ggtitle("Barrel Unknown for Hamby173")

crosscuts %>% 
  filter(Set == "Hamby252" & Barrel == "Unknown") %>%
    ggplot(aes(x = x, y = value)) + 
      geom_line() +
        facet_grid(Bullet~Land, labeller="label_both") +
          theme_bw()+ ggtitle("Barrel Unknown for Hamby252")

crosscuts %>% filter(id == "Hamby252-Unknown-B-2") %>% 
  ggplot(aes(x = x, y = value))+
    geom_line()+
      facet_grid(Bullet~Land + Set, labeller = "label_both")+
        theme_bw() + ggtitle("High CrossSection Bullet B")


```

Looking at the CrossCuts we can see the side profile for a bullets land impression for every barrel in Hamby173 and Hamby252.  For most of the CrossCuts the shoulders can be clearly identified but there are some that can not be "clearly" identified due to possbile tank rash, pitting, or scans that do not meet the standards that forensic analysis require.  I can not say for certain if there are scans that should be excluded.  I used FIX3P to examine the "groove to groove" scans and noticed considerable tank rash on some of the scans.  There was some noticeable pitting as well but I only felt it was a concern when the pitting was concentrated in the center of the "groove to groove" scan.

When looking at the Crosscuts we can see most have noticeable curvature.  There are some scans that do not and these scans can look like a flat line or even a traingle... I Have made note of these particular scans as well.  


# Groved Data taken from github
```{r}
#Grooves
saved_grooves_location <- "V2H173_H252_Grooves_data.rda"
if (file.exists(saved_grooves_location)) {
  hamby$Grooves <- readRDS(saved_grooves_location)
} else {
  hamby <- hamby %>% 
    mutate(Grooves = CrossCut %>% 
             future_map(.f = cc_locate_grooves, 
                        method = "rollapply", smoothfactor = 15, return_plot = T))  # use plot so that the shiny app works...
}

grooves <- hamby %>% tidyr::unnest(Grooves)

head(grooves, 10)

head(select(hamby, -path, -x3p, -CrossCut), 5)


plan(sequential) # stop furrr multicore processes - messes with shiny/rmd
```


# Examining Groove Cut Offs
```{r}

Hamby_test <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 6)

Hamby_test2 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 3 & Bullet == 1)

Hamby_test3 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 1 & Bullet == 1)

Hamby_test4 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == 9 & Bullet == 2)

Hamby_test5 <- hamby %>% 
  filter(Set == "Hamby252") %>% 
    filter(Barrel == "Unknown") %>% 
      filter(Bullet == "B" | Bullet == "S" | Bullet == "U")

Hamby_test6 <- hamby %>% 
  filter(Set == "Hamby173") %>% 
    filter(Barrel == 3 & Bullet == 2)

Hamby_test7 <- hamby %>% 
  filter(Set == "Hamby173") %>% 
    filter(Barrel == "Unknown") %>% 
      filter(Bullet == "B" | Bullet == "E" | Bullet == "U")


gridExtra::grid.arrange(Hamby_test$Grooves[[1]]$plot,
                        Hamby_test$Grooves[[7]]$plot,
                         Hamby_test2$Grooves[[4]]$plot,
                         Hamby_test3$Grooves[[6]]$plot,
                         Hamby_test4$Grooves[[4]]$plot,
                         Hamby_test5$Grooves[[2]]$plot,
                         Hamby_test5$Grooves[[10]]$plot,
                        nrow = 2)
                        
                        

                        
gridExtra::grid.arrange(Hamby_test6$Grooves[[1]]$plot,
                        Hamby_test7$Grooves[[3]]$plot,
                        Hamby_test7$Grooves[[15]]$plot,
                        Hamby_test7$Grooves[[12]]$plot,
                        nrow = 2)

rm(Hamby_test, Hamby_test2, Hamby_test3, Hamby_test4, Hamby_test5, Hamby_test6, Hamby_test7 )
```


# When run in interactive mode, a shiny app can be used to set smarter grooves.
# Grooves taken from github. Played around with shiny but did not use.
```{r get-grooves-interactive, echo = FALSE}
library(shiny)
if (file.exists(saved_grooves_location)) {
  hamby$Grooves <- readRDS(saved_grooves_location)
}
if (interactive()) { # only run when you're manually running chunks... don't run when the whole document is compiled.
  shinyApp(
    ui = fluidPage(
      selectInput("k", "Investigate kth plot:",
                  selected = 1,
                  choices = (1:length(hamby$Grooves)) %>% set_names(hamby$id)
      ),
      textOutput("groovelocations"),
      actionButton("confirm", "Confirm"),
      actionButton("save", "Save"),
      plotOutput("groovePlot", click = "plot_click"),
      verbatimTextOutput("info")
    ),
    
    server = function(input, output, session) {
      output$groovePlot <- renderPlot({
        k <- as.numeric(input$k)
        p <- hamby$Grooves[[k]]$plot
        
        p
      })
      output$groovelocations <- renderText({
        paste(
          "Left Groove: ", hamby$Grooves[[as.numeric(input$k)]]$groove[1],
          " Right Groove: ", hamby$Grooves[[as.numeric(input$k)]]$groove[2]
        )
      })
      observeEvent(input$confirm, {
        cat(paste(hamby$id[as.numeric(input$k)], "\n"))
        updateSelectInput(session, "k", "Investigate kth plot:",
                          selected = as.numeric(input$k) + 1,
                          choices = (1:length(hamby$Grooves)) %>% set_names(hamby$id)
        )
      })
      observeEvent(input$save, {
        saveRDS(hamby$Grooves, file = saved_grooves_location)
        message("groove data saved\n")
      })
      
      observeEvent(input$plot_click, {
        k <- as.numeric(input$k)
        xloc <- input$plot_click$x
        
        gr <- hamby$Grooves[[k]]$groove
        if (abs(gr[1] - xloc) < abs(gr[2] - xloc)) {
          hamby$Grooves[[k]]$groove[1] <<- xloc
        } else {
          hamby$Grooves[[k]]$groove[2] <<- xloc
        }
        output$groovePlot <- renderPlot({
          k <- as.numeric(input$k)
          p <- hamby$Grooves[[k]]$plot +
            geom_vline(xintercept = hamby$Grooves[[k]]$groove[1], colour = "green") +
            geom_vline(xintercept = hamby$Grooves[[k]]$groove[2], colour = "green")
          
          p
        })
      })
      output$info <- renderText({
        paste0("x=", input$plot_click$x, "\ny=", input$plot_click$y)
      })
    },
    options = list(height = 500)
  )
  saveRDS(hamby$Grooves, file = saved_grooves_location)
} else {
  if (!file.exists(saved_grooves_location)) {
    message("run script in interactive mode to fix grooves")
  } else {
    hamby$Grooves <- readRDS(saved_grooves_location)
  }
}


#Test Some Grooves(performed:06/12/19)
```

```{r}
#Signatures
hamby <- hamby %>% mutate(Signatures = future_map2(.x = CrossCut, .y = Grooves, .f = cc_get_signature, span = 0.75, span2 = .03)) 
Signatures <- hamby %>% select(id, Set, Barrel, Bullet, Land, Signatures) %>% tidyr::unnest()
head(Signatures, 5)

```

```{r}
#Looking for major issues - grooves not set correctly (large deviations at beginning or end of a line)
Signatures %>%
  filter(Barrel != "Unknown") %>% 
ggplot(data = ., aes(x = x, y = sig, color = Land)) + 
  geom_line() + 
  facet_grid(Set + paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))# put the barrels in the right order

Signatures %>%
  filter(Barrel != "Unknown") %>% 
ggplot(data = ., aes(x = x, y = sig, color = Bullet)) + 
  geom_line() + 
  facet_grid(Set + paste("Bullet", Bullet) ~ sprintf("Barrel %02s", Barrel))# Notice the difference

Signatures %>% 
  filter(Barrel == 1) %>% 
    filter(Set == "Hamby173") %>%
      ggplot(aes(x = x, y = sig, color = id))+
        geom_line() + facet_wrap(~Bullet)+ theme_bw()

Signatures %>% 
  filter(Barrel == 9) %>% 
    filter(Set == "Hamby173") %>%
      ggplot(aes(x = x, y = sig, color = id))+
        geom_line() + facet_wrap(~Bullet) + theme_bw()

Signatures %>% 
  filter(Barrel == 10) %>% 
    filter(Set == "Hamby173") %>%
      ggplot(aes(x = x, y = sig, color = id))+
        geom_line() + facet_wrap(~Bullet) + theme_bw()

#-------------------------------------------------------------------------------------------------------
Signatures %>% 
  filter(Barrel == 1) %>% 
    filter(Set == "Hamby252") %>%
      ggplot(aes(x = x, y = sig, color = id))+
        geom_line() + facet_wrap(~Bullet) + theme_bw()

Signatures %>% 
  filter(Barrel == 6) %>% 
    filter(Set == "Hamby252") %>%
      ggplot(aes(x = x, y = sig, color = id))+
        geom_line() + facet_wrap(~Bullet) + theme_bw()

Signatures %>% 
  filter(Barrel == 10) %>% 
    filter(Set == "Hamby252") %>%
      ggplot(aes(x = x, y = sig, color = id))+
        geom_line() + facet_wrap(~Bullet) + theme_bw()

#qplot(data = filter(Signatures, id %in% unique(id)[1:6]), x = x, y = sig, geom = "line", color = id) # Plot a few to see what they look like


```
Examining the Signature Profiles we can see for barrels 1-10 and for both Hamby173 + Hamby252, that the signatures for lands 1-6 are aligned pretty well.  There seems to be some noticeable deviations at the beginning and end for Barrels 1-10 in both sets. I looked at the groove to groove scans using FIX3P and these spikes at the beginning and end for Barrels 1 and 10 can be identified.  Groove locations seem to be set correctly for these lands.  

There is some noticeable missing data for Signature comparisons [Hamby252/Bullet1] when filling by Bullet.  This is hard to see when filling by the Lands.

```{r}
comparisons <- crossing(Bullet1 = hamby$id, Bullet2 = hamby$id) %>%
  left_join(nest(hamby, -id) %>% magrittr::set_names(c("Bullet1", "Bullet1_data"))) %>%
  left_join(nest(hamby, -id) %>% magrittr::set_names(c("Bullet2", "Bullet2_data"))) %>%
  mutate(Set1 = str_extract(Bullet1, "Hamby\\d{2,3}"),
         Set2 = str_extract(Bullet2, "Hamby\\d{2,3}")) %>%
  filter(Set1 == Set2) %>% # Get rid of cross-set comparisons for now...
  select(-matches("Set"))
head(comparisons)
```

```{r}
#plan(multicore(workers = availableCores(constraints = 8)))

get_sig <- function(data) {
  purrr::map(data$Signatures, "sig")
}
comparisons <- comparisons %>%
  mutate(sig1 = purrr::map(Bullet1_data, get_sig), sig2 = purrr::map(Bullet2_data, get_sig))

plan(multicore)

comparisons <- comparisons %>%
  mutate(Aligned = future_map2(sig1, sig2, ~sig_align(unlist(.x), unlist(.y))))

# Get striae
comparisons <- comparisons %>%
  mutate(Striae = future_map(Aligned, sig_cms_max))

saveRDS(select(comparisons, -Bullet1_data, -Bullet2_data), file = "Hamby_173_252_Comparisons.rda")

```

# Extracting features
```{r}
comparisons <- comparisons %>% 
  select(-Bullet1_data, -Bullet2_data)

plan(multicore(workers = availableCores(constraints = 8)))

comparisons <- comparisons %>% 
  mutate(features = future_map2(.x = Aligned, .y = Striae, .f = extract_features_all, resolution = 1.5625))

comparisons <- comparisons %>% 
  mutate(Legacy_Features = future_map(Striae, extract_features_all_legacy, resolution = 1.5625))

comparisons <- comparisons %>% 
  tidyr::unnest(Legacy_Features)

head(comparisons)
```


# Creating Columns for organization and for future plotting purposes.
```{r}
comparisons <- tibble::rowid_to_column(comparisons, "Index")

comparisons <- comparisons %>% 
  mutate(Set = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\1", Bullet2))
comparisons <- comparisons %>% 
  mutate(BarrelA = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\2", Bullet2))
comparisons <- comparisons %>% 
  mutate(BarrelB = gsub("(Hamby173|Hamby252)-([0-9]{0,2}|Unknown)-([1-2A-Z])-([1-6])", "\\2", Bullet1))
comparisons <- comparisons %>% 
  mutate(BulletA = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\3", Bullet2))
comparisons <- comparisons %>% 
  mutate(BulletB = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\3", Bullet1))
comparisons <- comparisons %>% 
  mutate(LandA = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\4", Bullet2))
comparisons <- comparisons %>% 
  mutate(LandB = gsub("(Hamby173|Hamby252)-([0-9]{1,2}|Unknown)-([1-2A-Z])-([1-6])", "\\4", Bullet1))

head(comparisons, 50)

```

```{r}
comparisons %>% select(ccf, cms, non_cms, matches, mismatches, D, sum_peaks) %>% summary()

comparisons <- comparisons %>% 
  mutate(KM_KNM = if_else(ccf >= 0.75, "Known_Match", "Known_non_Match")) %>% 
    mutate(KM_KNM = factor(KM_KNM))

HambyDataLong <- gather(comparisons, key="measure", value="value", c("ccf", "cms", "non_cms", "matches", "mismatches", "D", "sum_peaks"))

HambyDataLong %>% 
    ggplot(aes(value, fill = KM_KNM))+
      geom_density(position = "identity", alpha = 0.50)+
        facet_wrap(~measure, ncol = 4, scale = "free")+
          scale_fill_brewer(palette = "Paired") + theme_bw()+
            ggtitle("Marginal Density for Features")

HambyDataLong %>% 
    ggplot(aes(value, fill = KM_KNM))+
      geom_density(position = "identity", alpha = 0.50)+
        facet_wrap(~measure + Set, ncol = 4, scale = "free")+
          scale_fill_brewer(palette = "Paired") + theme_bw()+
            ggtitle("Marginal Density for Features")

head(HambyDataLong)

rm(HambyDataLong) # File size is large, just for  convenience sake.

```

Looking at the summary statistics for some of the features extracted we can see important observations. The ccf has a minimum value of .0489, a mean of .3577, and a Maximum value of 1.  For Consecutively Matching Striae we see a minumum value of 0, a mean of 1.049, and a Maximum of 15.9357.  For non Consecutively Matching Striae we see a minimum value of 0, a mean of 6.135, and a maximum of 20.408. For # matches we have a minimum value of 0, a mean of 1.611, and a maximum of 15.9357. For # mismatches we have a minimum value of 0, a mean of 10.390, and a maximum of 20.408.  For average Distance (D) we have a minimum value of 0, a mean of .003341, and a maximum value of .02. For sum_peaks we have a minimum value of 0, a mean of 2.921, and a maximum of 44.036. 

We now create a density plot.  First we had to define a "Known Match" and a "Known non Match."  Standard procedure for a "Known" match/nonmatch is if the ccf is greater than or equal to .50, then it is a Known match.  If the ccf is less than .50, it is a known nonmatch.  From the Density plot, the first things that strike concerns are the scaling of the x and y axes.  The second thing to notice is that seperation in the density plots only starts to occur when the ccf condition for a Known match/nonmatch increases from .50 to around .70 and up.  I also plotted the Density Plots by "Set" but separation did not occur until ccf condition was increased to .70's. 

```{r}
comparisons$rfscore <- predict(rtrees, newdata = comparisons, type = "prob")[,2]
head(comparisons)

Bullet_Scores <- comparisons %>% 
  group_by(BulletA, BulletB) %>% 
    tidyr::nest()

Bullet_Scores <- Bullet_Scores %>% 
  mutate(Bullet_Score = data %>% 
          future_map_dbl(.f = function(d) max(compute_average_scores(land1 = d$LandA, land2 = d$LandB, d$rfscore))))

Bullet_Scores %>% select(-data) %>% arrange(desc(Bullet_Score))

Bullet_Scores <- Bullet_Scores %>% 
  mutate(data = data %>% future_map(.f = function(d){
  d$samepath = bullet_to_land_predict(land1 = d$LandA, land2 = d$LandB, d$rfscore, difference = 0.1)
  d
}))

Bullet_Scores %>% tidyr::unnest(data) 
```





# Comparing rfscores
```{r}
library(gridExtra)
head(comparisons)

plot1 = comparisons %>%
  filter(BarrelA == 10 & BarrelB == 10) %>% 
    filter(BulletA == 1 & BulletB == 1 ) %>% 
      ggplot(aes(x = LandA, y = LandB, fill = rfscore))+ 
        geom_tile()+ 
          scale_fill_gradient2(low = "#000000", high = "#56B4E9", midpoint = 0.5) +facet_grid(BulletB~BulletA, labeller = "label_both")+ 
            xlab("Land A") + ylab("Land B") + theme(aspect.ratio = 1)+ ggtitle("Same Source and Same Bullet")+ facet_grid(~Set)

plot2 = comparisons %>%
  filter(BarrelA == 10 & BarrelB == 10) %>% 
    filter(BulletA == 1 & BulletB == 2 ) %>% 
      ggplot(aes(x = LandA, y = LandB, fill = rfscore))+ 
        geom_tile()+ 
          scale_fill_gradient2(low = "#000000", high = "#56B4E9", midpoint = 0.5)+
            facet_grid(BulletB~BulletA, labeller = "label_both")+ 
            xlab("Land A") + ylab("Land B") + theme(aspect.ratio = 1)+ 
              ggtitle("Same Source but Different Bullet") + facet_grid(~Set)


plot3 = comparisons %>% 
  filter(BarrelA == 10 & BarrelB == 5) %>% 
    filter(BulletA == 1 & BulletB == 2 ) %>% 
      ggplot(aes(x = LandA, y = LandB, fill = rfscore))+ 
        geom_tile()+ 
          scale_fill_gradient2(low = "#000000", high = "#56B4E9", midpoint = 0.5)+
            facet_grid(BulletB~BulletA, labeller = "label_both")+ 
            xlab("Land A") + ylab("Land B") + theme(aspect.ratio = 1)+ 
              ggtitle("Different Source") + facet_grid(~Set)

grid.arrange(plot1, plot2, plot3, ncol = 2)

```

Looking at the land-land matching scores for bullets 1 and 2. We plotted an example when the bullets came from the same barrel and when the bullets came from different barrels. The matrix shown for bullets 1 and 2 that came from the same barrel look promising but rfscores seem lower than expected.



#Statistical Summary Comparions between bulletxtrctr demo and Refit_Analysis

```{r}
comparisons %>% 
  select(ccf, rough_cor, D, signature_length, matches, mismatches, cms, non_cms, sum_peaks, rfscore) %>% 
    summary()

```


I wanted to see how the summary statistics for certain features compared with the bulletxtrctr demo and Refit_Analysis.  The results were pretty similar even though the data for Refit_Analysis is much bigger than the bulletxtrctr demo.  There were some noticeable difference though:
  
The Max Distance for Refit_Analysis was .02, while the max distance for bulletxtrctr demo was .005

Matches and Mismatches varied a little for both but showed very similar outputs.

For Bulletxtrctr demo the cms had a mean of 1.6845 and a max of 9.5188.  The non_cms had a mean of 3.531 and a max of 8.457.
For Refit_Analysis the cms had a mean of 1.0509 and a max of 15.9357.  The non_cms had a mean of 6.144 and a max of 20.408. 

The mean rfscore for bulletxtrctr demo was 0.189329.
The mean rfscore for Refit_Analysis was 0.093215.  

```{r}
head(comparisons)
head(Signatures)

comparisons %>% filter(KM_KNM == "Known_Match" & rfscore <= .50) %>% arrange(rfscore)

Signatures %>% 
  filter(id == "Hamby173-10-2-1" | id == "Hamby173-Unknown-I-6") %>% 
    ggplot(aes(x = x, y = sig, color = id))+
      geom_line()+ 
        facet_wrap(~Bullet)+ 
          theme_bw() #Known Match and low rfscore


Signatures %>% 
  filter(id == "Hamby252-Unknown-C-2" | id == "Hamby252-1-2-6") %>% 
    ggplot(aes(x = x, y = sig, color = id))+
      geom_line()+ 
        facet_wrap(~Bullet)+ 
          theme_bw() #Known non Match and high rfscore

```

